

# Skin effect evaluation - report

***

&nbsp;


```{r, echo=FALSE,  warning = FALSE }

loc = (data_to_report()$well_location != "")
```


Evaluated on `r data_to_report()$time`.

Name of the well: `r data_to_report()$name`.

`r if(loc){"Location of the well:" }`
`r if(loc){ data_to_report()$well_location }`



&nbsp;

&nbsp;

&nbsp;


The pumping test was evaluated to obtain the parameters of the aquifer and additional resistances. During the pumping test the pumped quantity was constant and the value was  **`r { as.character(data_to_report()$Q) }` m3/s**. The well parameters are shown in Table 1 and aquifer parameters in Table 2.


&nbsp;
&nbsp;

```{r , echo=FALSE, comment = NA, warning = FALSE, memory.limit(size = 60000), fig.width = 11, fig.height = 4}


library(grid)
library(gridExtra)
library(gtable)
minus_res = 0
 value <- c( data_to_report()$R, data_to_report()$well_stor, data_to_report()$well_depth, data_to_report()$additional_resistance, additional_from_slope(), skin_ef(), cd())
      units <- c("[m]",  "[-]", "[m]", "[m]", "[m]",  "[-]",  "[-]")
      names <- c( "Radius", "Storativity",  "Depth of well", "Additional resistance", "Additional resistance 2", "skin effect", "cd" )
        
         if(value[4] < 0)
      {
        value[4] = value[4] * -1
        minus_res = 1
      }
      
      na <- which(value > 0)
      
       if(  minus_res == 1)
         value[4]= value[4] * -1
      
      value <- value[na]
      units <- units[na]
      names <- names[na]
      
      table = data.frame(Value = value, Units = units)
      row.names(table) <- names
      minus_res = 0
      
     value2 <- c(data_to_report()$Trans, data_to_report()$Stor, data_to_report()$hydraulic_cond, data_to_report()$cone_of_depr, data_to_report()$aqua_thick)
      units2 <- c("[m2/s]", "[m-1]", "[m/s]", "[m]", "[m]")
      names2 <- c("Transmissivity", "Storativity", "Hydraulic conductivity", "Cone of depression", "Aquifer thickness")
      
      na2 <- which(value2 > 0)
      value2 <- value2[na2]
      units2 <- units2[na2]
      names2 <- names2[na2]
      
      table2 = data.frame(Value = value2, Units = units2)
      row.names(table2) <- names2

title <- textGrob("Table 1. well parameters",gp=gpar(fontsize = size_title()))
title2 <- textGrob("Table 2. aquifer parameters",gp=gpar(fontsize = size_title()))

tt3 <- ttheme_minimal(base_size = size_text(),
  core=list(bg_params = list(fill = blues9[2:5], col=NA)))

t1 <- tableGrob(table, rows = names, theme =  tt3)
t2 <- tableGrob(table2, rows = names2, theme = tt3)

padding <- unit(4,"mm")

table <- gtable_add_rows(
     t1, 
     heights = grobHeight(title) + padding,
     pos = 0)

table2 <- gtable_add_rows(
     t2, 
     heights = grobHeight(title2) + padding,
     pos = 0)

table <- gtable_add_grob(
    table, 
    title, 
    1, 1, 1, ncol(table),clip = "on")

table2 <- gtable_add_grob(
    table2, 
    title2, 
    1, 1, 1, ncol(table2),clip = "on")



# grid.arrange(
 # table,
 # table2,
 # respect=TRUE,
 # nrow = 1)

grid.arrange(
 table,
 table2,
 respect = TRUE,
 layout_matrix = matrix(c(1, 2), byrow = TRUE, nrow = 1),
widths = c(7,7), heights = c(3,3)
 )

```




```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
pdf = (mark_format() == "pdf")
```


```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
word = (mark_format() == "docx")
```

\newpage

```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
raw = sum(data_to_report()$report_contain == "Graph - input data") == 1
```


```{r, eval = raw, echo=FALSE,  warning = FALSE, fig.align ='center'}
asis_output("##  Graph - input data" )
```

&nbsp;

```{r , eval = raw, collapse=TRUE, echo=FALSE,comment = NA, fig.width = graph_size(), fig.asp = 0.5, fig.align ='left', warning = FALSE }

 plot_raw <- plot_grid(ggplot(data_to_report()$data_ok, aes(x = time,
                       y = drawdown,
                        col = "Observed values")) +
                       geom_point() + 
                       labs(x = "Time", y = "Drawdown")  +
     scale_color_manual(labels = "Observed values", values = "black") +
     labs(color = "") + 
                       theme(text = element_text(size = 18)))
   
plot_grid(plot_raw,  ncol = 1, scale =1)

```


&nbsp;

```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
data_fit = sum(data_to_report()$report_contain == "Graph - data used") == 1
```


```{r, eval = data_fit, echo=FALSE,  warning = FALSE, fig.align ='center'}
asis_output("###  Graph - data used for the evaluation" )
```


&nbsp;


```{r , eval = data_fit, collapse=TRUE, echo=FALSE,comment = NA, fig.width = 11, fig.asp = 0.5, fig.align ='left', warning = FALSE }

used_max = data_to_report()$max_data_used

plot.data_used <- (ggplot(data_ok()[1:end_for_report(), ], aes(x = time, y = drawdown)) +
                       geom_point() + scale_x_log10() +
                       labs(x = "Time",
                            y = "Drawdown") +
                       geom_point(data = data_ok()[min_val():used_max, ], aes(
                         x = time,
                         y = drawdown,
                         col = "Data used - fit")) +
                       labs(color = "")  +
     theme(text = element_text(size = 18)))
 
plot_grid(plot.data_used,  ncol = 1, scale = 1)

```





```{r , collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
graph_res = sum(data_to_report()$report_contain == "Graph - fitted values") == 1
```


&nbsp;

`r if(loc){ "&nbsp;" }`


```{r, eval = graph_res, echo=FALSE,  warning = FALSE}
asis_output("##  Graph - fitted values")
```

&nbsp;

```{r , eval = graph_res, collapse=TRUE, echo=FALSE,comment = NA, fig.width = graph_size(), fig.asp = 0.5, fig.align ='left', warning = FALSE }


plot.fitted <- (ggplot(data_to_report()$final_data[1:end_t(), ], aes(x = time, y = drawdown)) +
                       geom_point() + scale_x_log10() +
                       labs(x = "Time",
                            y = "Drawdown") +
                       geom_point(data = data_to_report()$fitted_data[1:end_t(), ], aes(
                         x = time,
                         y = drawdown,
                         col = "Fitted values")) +
                       labs(color = "")  +
     theme(text = element_text(size = 18)))
 
plot_grid( plot.fitted,  ncol = 1, scale = 1)



```



